\bf Fast, Scalable Phrase-Based SMT Decoding

### 2016-09-10 amta.2016/amta2016.tex
move to amta.2016

%\author{\name{\bf Hieu Hoang} \hfill  \addr{hieu@moses-mt.org}\\ 
%        \addr{Moses Machine Translation CIC, UK}
%\AND
%       \name{\bf Nicolay Bogoychev} \hfill \addr{s1031254@sms.ed.ac.uk}\\
%       \name{\bf Kenneth Heafield} \hfill \addr{kheafiel@inf.ed.ac.uk}\\
%        \addr{University of Edinburgh, Scotland}
%\AND
%       \name{\bf Lane Schwartz} \hfill \addr{lanes@illinois.edu}\\
%        \addr{University of Illinois, USA}
%\AND
%       \name{\bf Marcin Junczys-Dowmunt} \hfill \addr{junczys@amu.edu.pl}\\
%        \addr{Adam Mickiewicz University}
%}

@@

This paper is the first we know of that focuses on improving decoding speed on multicore servers. We take a holistic approach to solving this issue, creating a decoder that is optimized for multi-core processing speed by concentrating on four main areas:
\begin{enumerate}
  \item \vspace{-2 mm} Faster memory management of data-structures through the use of customized memory pools
  \item \vspace{-2 mm} Exploring alternatives to cardinality-based hypothesis stack configuration
  \item \vspace{-2 mm} Re-examining the efficiency of phrase-table lookup using translation rule caching and data compression
  \item \vspace{-2 mm} Integrating the lexicalized re-ordering model into the phrase-table, thus eliminating the need for independent random lookup this model 
\end{enumerate}
The result is a decoder that is significantly faster than the Moses baseline for single-threaded operation, and scales with the number of cores.

As far as possible, model scores and functionality are compatible with Moses to aid comparison and ease transition for existing users. All source code will be made available under an open-source license.

>>>>

\author{\name{\bf Hieu Hoang} \hfill  \addr{hieu@moses-mt.org}\\ 
        \addr{Moses Machine Translation CIC, UK}
\AND
       \name{\bf Nicolay Bogoychev} \hfill \addr{s1031254@sms.ed.ac.uk}\\
       %\name{\bf Kenneth Heafield} \hfill \addr{kheafiel@inf.ed.ac.uk}\\
        \addr{University of Edinburgh, Scotland}
\AND
       \name{\bf Lane Schwartz} \hfill \addr{lanes@illinois.edu}\\
        \addr{University of Illinois, USA}
\AND
       \name{\bf Marcin Junczys-Dowmunt} \hfill \addr{junczys@amu.edu.pl}\\
        \addr{Adam Mickiewicz University}
}

@@

This paper is the first we know of that focuses on improving decoding speed on multicore servers. We take a holistic approach to solving this issue, creating a decoder that is optimized for multi-core processing speed by concentrating on four main areas:
\begin{enumerate}
  \item \vspace{-2 mm} Faster memory management of data-structures through the use of customized memory pools
  \item \vspace{-2 mm} Exploring alternatives to cardinality-based hypothesis stack configuration
  \item \vspace{-2 mm} Re-examining the efficiency of phrase-table lookup using translation rule caching and data compression
  \item \vspace{-2 mm} Integrating the lexicalized re-ordering model into the phrase-table, thus eliminating the need for independent random lookup this model 
\end{enumerate}

The result is a decoder that is significantly faster than the Moses baseline for single-threaded operation, and scales with the number of cores.

We will maintain the Moses decoder's embarrassingly parallel, one sentence-per-thread decoding framework. As far as possible, model scores and functionality are compatible with Moses to aid comparison and ease transition for existing users. The source code is available in the existing Moses repository\footnote{\scriptsize https://github.com/moses-smt/mosesdecoder/tree/master/contrib/moses2}.
